---
title: "duplicate data?"
author: "Min-Yang Lee"
date: "11/05/2024"
output:
  html_document: default
  pdf_document: default
urlcolor: blue
---
# Project setup
here(), load libraries, and set a data vintage.  


```{r setup, echo=FALSE, results=FALSE}
# Set Path
here::i_am("R_code/data_duplications.rmd")
library("here")
library("ROracle")
library("tidyverse")
library("lubridate")
library("readr")
library("kableExtra")

#Data vintage
vintage_string<-Sys.Date()
vintage_string<-gsub("-","_",vintage_string)

#############################################################################
#knitr options

knitr::opts_chunk$set(echo=FALSE, warning = FALSE, error = FALSE, message = FALSE, comment = FALSE, cache = FALSE, progress = TRUE, verbose = FALSE, 
											dpi = 600)
options(tinytex.verbose = TRUE)
# options(knitr.table.format = "latex")


# Set up paths.
```

# Overview

I think there may be some "duplicated" records in CFDBS tables.  These look like they are entered late



# Dependencies

This code depends on:

1.  The ability to connect to NEFSC oracle databases (CAMS, NEFSC_GARFO, CFDERS).


# Data Overview

Data Comes from CAMS_LAND, NEFSC_GARFO.CFDERS_ALL_YEARS, and CFDBS.CFDERS2021.

I'm pulling just rows where the "state commercial fishing license" is 2147.

the CAMS version of AA doesn't have the state commercial fishing license column.



```{r data_query, echo=TRUE,eval=TRUE}
star_dbi_ROracle <- DBI::dbConnect(dbDriver("Oracle"),id, password=novapw, dbname=nefscusers.connect.string)



# CAMS
CURRENT.QUERY <- "select * from cams_land where dlr_cflic='2147' and year=2021 and itis_tsn='167687' order by dlr_date"
CAMS_data<-dplyr::tbl(star_dbi_ROracle,sql(CURRENT.QUERY)) %>%
   collect() 

CAMS_data<-CAMS_data %>%
  relocate(any_of(c("STATUS", "CAMSID", "DLR_DATE", "DLRID", "DLR_STID","DLR_CFLIC", "PERMIT", "HULLID", "LNDLB", "LIVLB", "VALUE", "DERSOURCE", "LINK")))




# CFDERS_ALL_YEARS
CURRENT.QUERY <- "select * from nefsc_garfo.cfders_all_years where nespp3=335 and year=2021 and cf_license='2147' order by year, month, day"
DERS_ALL_YEARS<-dplyr::tbl(star_dbi_ROracle,sql(CURRENT.QUERY)) %>%
   collect()

DERS_ALL_YEARS<-DERS_ALL_YEARS %>%
  relocate(any_of(c("YEAR", "MONTH", "DAY", "DEALNUM", "STATE_DNUM", "CF_LICENSE", "PERMIT", "HULLNUM", "SPPLNDLB", "SPPLIVLB", "SPPVALUE", "DERSOURCE", "LINK", "DOE","DDATE","DOC")))


# CFDBS.CFDERS2021
CURRENT.QUERY <- "select * from cfdbs.cfders2021 where nespp3=335 and year=2021 and month=1 and state=49 order by day"

DERS2021<-dplyr::tbl(star_dbi_ROracle,sql(CURRENT.QUERY)) %>%
   collect()
DERS2021<-DERS2021 %>%
  relocate(any_of(c("YEAR", "MONTH", "DAY", "DEALNUM", "STATE_DNUM", "CF_LICENSE", "PERMIT", "HULLNUM", "SPPLNDLB", "SPPLIVLB", "SPPVALUE", "DERSOURCE", "LINK","DOE")))


# CAMS CFDETS AA
CURRENT.QUERY<-  "select * from CAMS_CFDETS_AA where itis_tsn='167687' and year=2021 and month=1 and state=49 order by day, link" 


CAMS_DETS_AA<-dplyr::tbl(star_dbi_ROracle,sql(CURRENT.QUERY)) %>%
   collect()


CAMS_DETS_AA<-CAMS_DETS_AA %>%
  relocate(any_of(c("CAMSID","YEAR", "MONTH", "DAY", "DEALNUM", "STATE_DNUM", "CF_LICENSE", "PERMIT", "HULLNUM", "SPPLNDLB", "SPPLIVLB", "SPPVALUE", "DERSOURCE", "LINK", "DOE", "STATUS")))

dbDisconnect(star_dbi_ROracle)


```




# CAMS

```{r CAMS, results=TRUE, eval=TRUE}
CT<-CAMS_data %>%
  head(10) %>%
  select(any_of(c( "DLR_DATE", "DLRID", "DLR_STID","DLR_CFLIC", "PERMIT", "HULLID", "LNDLB", "LIVLB", "VALUE", "DERSOURCE", "LINK","STATUS", "CAMSID")))
kbl(CT, digits=0,booktabs=T, align=c("l",rep('r',times=10)), caption =  "Select data from CAMS") %>%
    kable_styling(full_width = T,latex_options = "hold_position") %>% 
      row_spec(0,bold=FALSE) 
```
I believe the first row here duplicates the next 4.  Summing the LNDLB and LIVLB for rows 2 through 5 produces the same values as the first row.  The "Commerical Fishing License" is the same, the hullid is the same, and the dealer date differs by just 1 day. 

The same is true for the next group of rows (row 6 compared to rows 7:10).

```{r CFDERS_ALL_YEARS, results=TRUE, eval=TRUE}
DERS_AY<-DERS_ALL_YEARS %>%
  head(10) %>%
  select(any_of(c("YEAR", "MONTH", "DAY", "DEALNUM", "STATE_DNUM", "CF_LICENSE", "PERMIT", "HULLNUM", "SPPLNDLB", "SPPLIVLB", "SPPVALUE", "DERSOURCE", "LINK", "DOE")))

kbl(DERS_AY, digits=0,booktabs=T, align=c("l",rep('r',times=13)), caption =  "Select data from CFDERS_ALL_YEARS") %>%
    kable_styling(full_width = T,latex_options = "hold_position") %>% 
      row_spec(0,bold=FALSE) 



test<-DERS_ALL_YEARS %>%
  dplyr::filter(MONTH=="01")%>%
  dplyr::filter(DERSOURCE=="WHSE") %>%
  summarise(total_land=sum(SPPLNDLB),
  total_live=sum(SPPLIVLB)
)


```

The same problem occurs in the CFDERS_ALL_YEARS version of the table. CF_License and hullnum match,spplndlb and spplivlb sum up, and the date differs by 1 day.  The DERSOURCE is WHSE and the entry date of the aggregate observation is in 2023.


```{r DERS2021, results=TRUE, eval=TRUE}
DER<-DERS2021 %>%
  head(10) %>%
  select(any_of(c("YEAR", "MONTH", "DAY", "DEALNUM", "STATE_DNUM", "CF_LICENSE", "PERMIT", "HULLNUM", "SPPLNDLB", "SPPLIVLB", "SPPVALUE", "DERSOURCE", "LINK", "DOE")))


kbl(DER, digits=0,booktabs=T, align=c("l",rep('r',times=12)), caption =  "Select data from CFDBS.CFDERS2021") %>%
    kable_styling(full_width = T,latex_options = "hold_position") %>% 
      row_spec(0,bold=FALSE) 

```
Regular CFDERS is different.  I'm pretty sure missing things are aggregated into day=0, but I'm not 100% sure.  The aggregate entry comes in 2022.

```{r CAMS_DETS2021, results=TRUE, eval=TRUE}
CAM_DETSAA<-CAMS_DETS_AA %>%
   head(12) %>%
  select(any_of(c("YEAR", "MONTH", "DAY", "DEALNUM", "STATE_DNUM", "CF_LICENSE", "PERMIT", "HULLNUM", "SPPLNDLB", "SPPLIVLB", "SPPVALUE", "DERSOURCE", "LINK", "STATUS","CAMSID")))

kbl(CAM_DETSAA, digits=0,booktabs=T, align=c("l",rep('r',times=12)), caption =  "Select data from CAMS CFDETS") %>%
    #column_spec(5:8, width = "2cm")
    kable_styling(full_width = T,latex_options = "hold_position") %>% 
      row_spec(0,bold=FALSE) 


```
Since I can't filter using cf_license, this show some extra rows that are not necessarily a concern.

I only set out to investigate the story with some of the Unclassified Market category, so I don't know how whether this is a single vessel-dealer or a more systematic problem. 


# R Session Information
```{r session_info, include=TRUE, echo=TRUE, results=TRUE, eval=TRUE}
sessionInfo()
Sys.Date()

```
This may be useful for diagnosing and troubleshooting one day.


